Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-17 MCQMC2022ChallengesQMCSoftwareArticle.tex
Fred 2023 Mac 14 Updates

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{cantileveredbeamwords.eps}
    \includegraphics[width=0.7\textwidth]{ldparallelbeam.eps}
    \caption{The expected deflection of a cantilevered beam with random Young's modulus.  QMCPy computes the answer in serial and in parallel using UM-Bridge and docker containers.  For small error tolerances, the time and sample size is $\calO(\varepsilon^{-1})$, and parallel processing gives a speed-up factor of four to five. These plots may be reproduced using the Jupyter notebook \SCComment{(1) Add url or citation. (2) What is the meaning of min and sec on the y-axis of lower left graph (The label says (s), which means seconds right?)? Are there numerical values on (left and right) y-axis? (3) The font size of the axis labels for the lower graphs could be made larger more like the top graph. (4) I guess the blue colors are covered by the orange colors in the bottom right graph. Maybe we can use blue crosses and orange broken lines instead.}}
    \label{fig:beam}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{cantileveredbeamwords.eps}
    \includegraphics[width=1\textwidth]{ldparallelbeam.eps}
    \caption{The expected deflection of a cantilevered beam with random Young's modulus.  QMCPy computes the answer in serial and in parallel using UM-Bridge and docker containers.  For small error tolerances, the time and sample size is $\calO(\varepsilon^{-1})$, and parallel processing gives a speed-up factor of four to five. These plots may be reproduced using the Jupyter notebook \url{https://github.com/QMCSoftware/QMCSoftware/blob/develop/demos/talk_paper_demos/MCQMC2022_Article_Figures.ipynb}  }
    \label{fig:beam}
\end{figure}
